Named Entity Recognition as Structured Prediction

### 2012-11-09 doc/report/paper.tex
Merge+minor changes.

\begin{abstract}
This paper describes an approach to \namedentity Recognition using Structured Prediction. The System was applied to four different languages: Spanish, Dutch, English and
German. Various sets of features were employed among them a Gazetteer feature that obtained a look-up list from the database DBPedia and which proved very useful.
The results were...
\end{abstract}

@@

\paragraph*{Gazetteer Features}
In order to create gazetteer lists for the more common named entities, we designed a \emph{SPARQL} query, that would retrieve entries from \emph{DBPedia} for all
languages. The reliability of the respective list is learnt be the perceptron.

@@

\begin{table}[h!]
\scriptsize
\begin{tabular}{| l | l l l| l l l |}

\hline
\bf Language & \multicolumn{3}{c|}{ \bf Test A}&\multicolumn{3}{c|}{ \bf Test B}\\
             & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\hline
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table}

>>>>

\begin{abstract}
Named Entity Recognition is a task

\end{abstract}

@@

\paragraph*{Gazetteer Features}
A technique commonly used in Named Entity Recognition is the use of external lists of names of a specific type (gazetteer). In order to create gazetteer lists for the more common named entities, we use a \emph{SPARQL} query to retrieve entries from \emph{DBpedia} for all required languages.

\begin{figure}
\begin{verbatim}
PREFIX dbp: <http://dbpedia.org/ontology/>
SELECT ?label
WHERE {
    ?entity rdf:type dbp:CLASS.
    ?entity rdfs:label ?label.
    FILTER (lang(?label) = LANGUAGE)
}
\end{verbatim}
\caption{SPARQL query for retrieving names of the class \texttt{CLASS} from DBpedia.}
\end{figure}

@@

\begin{table*}[t]
\centering
\begin{tabular}{| l | l l l| l l l |}

\hline
\bf Language & \multicolumn{3}{c|}{ \bf Test A}&\multicolumn{3}{c|}{ \bf Test B}\\
             & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\hline
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table*}
